A Logistic Regression Approach to CoIL Challenge 2000

### 2019-11-11 final project/Manuscript.Rmd
Updated Final Project with data dictionary

```{r setup, include = FALSE}
# Documentation at https://crsh.github.io/papaja_man/
# If you have no use for TeX beyond rendering R Markdown documents, I recommend you use TinyTex.
# install.packages("tinytex")
# tinytex::install_tinytex()
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")
library("papaja")

library(tidyverse)

@@

# Appendices
<!--
- Supplemental tables and/or figures.
-->
## R statistical programming code.

@@

>>>>

```{r setup, include = FALSE}
# Documentation at https://crsh.github.io/papaja_man/
# If you have no use for TeX beyond rendering R Markdown documents, I recommend you use TinyTex.
# install.packages("tinytex")
# tinytex::install_tinytex()
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")
library("papaja")
library(kableExtra)
library(tidyverse)

@@

# Appendices

<!--
- Supplemental tables and/or figures.
-->

## R statistical programming code.

@@

\newpage
## Data Dictionary

```{r, results='asis'}
data_dictionary <- data.frame(
  Name=c("MOSTYPE", "MAANTHUI", "MGEMOMV", "MGEMLEEF", "MOSHOOFD", "MGODRK", "MGODPR", "MGODOV", "MGODGE", "MRELGE", "MRELSA", "MRELOV", "MFALLEEN", "MFGEKIND", "MFWEKIND", "MOPLHOOG", "MOPLMIDD", "MOPLLAAG", "MBERHOOG", "MBERZELF", "MBERBOER", "MBERMIDD", "MBERARBG", "MBERARBO", "MSKA", "MSKB1", "MSKB2", "MSKC", "MSKD", "MHHUUR", "MHKOOP", "MAUT1", "MAUT2", "MAUT0", "MZFONDS", "MZPART", "MINKM30", "MINK3045", "MINK4575", "MINK7512", "MINK123M", "MINKGEM", "MKOOPKLA", "PWAPART", "PWABEDR", "PWAAND", "PPERSAUT", "PBESAUT", "PMOTSCO", "PVRAAUT", "PAANHANG", "PTRACTOR", "PWERKT", "PBROM", "PLEVEN", "PPERSONG", "PGEZONG", "PWAOREG", "PBRAND", "PZEILPL", "PPLEZIER", "PFIETS", "PINBOED", "PBYSTAND", "AWAPART", "AWABEDR", "AWALAND", "APERSAUT", "ABESAUT", "AMOTSCO", "AVRAAUT", "AAANHANG", "ATRACTOR", "AWERKT", "ABROM", "ALEVEN", "APERSONG", "AGEZONG", "AWAOREG", "ABRAND", "AZEILPL", "APLEZIER", "AFIETS", "AINBOED", "ABYSTAND", "CARAVAN"),
  Description = c("Customer Subtype", "Number of houses", "Avg size household", "Avg age", "Customer main type", "Roman catholic", "Protestant", "Other religion", "No religion", "Married", "Living together", "Other relation", "Singles", "Household without children", "Household with children", "High level education", "Medium level education", "Lower level education", "High status", "Entrepreneur", "Farmer", "Middle management", "Skilled labourers", "Unskilled labourers", "Social class A", "Social class B1", "Social class B2", "Social class C", "Social class D", "Rented house", "Home owners", "1 car", "2 cars", "No car", "National Health Service", "Private health insurance", "Income < 30.000", "Income 30-45.000", "Income 45-75.000", "Income 75-122.000", "Income >123.000", "Average income", "Purchasing power class", "Contribution private third party insurance", "Contribution third party insurance (firms)", "Contribution third party insurane (agriculture)", "Contribution car policies", "Contribution delivery van policies", "Contribution motorcycle/scooter policies", "Contribution lorry policies", "Contribution trailer policies", "Contribution tractor policies", "Contribution agricultural machines policies", "Contribution moped policies", "Contribution life insurances", "Contribution private accident insurance policies", "Contribution family accidents insurance policies", "Contribution disability insurance policies", "Contribution fire policies", "Contribution surfboard policies", "Contribution boat policies", "Contribution bicycle policies", "Contribution property insurance policies", "Contribution social security insurance policies", "Number of private third party insurance", "Number of third party insurance (firms)", "Number of third party insurane (agriculture)", "Number of car policies", "Number of delivery van policies", "Number of motorcycle/scooter policies", "Number of lorry policies", "Number of trailer policies", "Number of tractor policies", "Number of agricultural machines policies", "Number of moped policies", "Number of life insurances", "Number of private accident insurance policies", "Number of family accidents insurance policies", "Number of disability insurance policies", "Number of fire policies", "Number of surfboard policies", "Number of boat policies", "Number of bicycle policies", "Number of property insurance policies", "Number of social security insurance policies", "Number of mobile home policy"))
#apa_table(data_dictionary, longtable = T, booktabs = T)
knitr::kable(data_dictionary, "latex", longtable = T) %>%
  kable_styling(latex_options = c("repeat_header"))
```

### 2019-11-11 final project/Manuscript.tex
Updated Final Project with data dictionary

@@

>>>>

Our investigation is similar to Doornik and Moyle (2000) in that we used a LOGIT model. \textbf{Reproduce his model and describe the results}

@@

\hypertarget{data-dictionary}{%
\subsection{Data Dictionary}\label{data-dictionary}}

\begin{longtable}{l|l}
\hline
Name & Description\\
\hline
\endfirsthead
\multicolumn{2}{@{}l}{\textit{(continued)}}\\
\hline
Name & Description\\
\hline
\endhead
MOSTYPE & Customer Subtype\\
\hline
MAANTHUI & Number of houses\\
\hline
MGEMOMV & Avg size household\\
\hline
MGEMLEEF & Avg age\\
\hline
MOSHOOFD & Customer main type\\
\hline
MGODRK & Roman catholic\\
\hline
MGODPR & Protestant\\
\hline
MGODOV & Other religion\\
\hline
MGODGE & No religion\\
\hline
MRELGE & Married\\
\hline
MRELSA & Living together\\
\hline
MRELOV & Other relation\\
\hline
MFALLEEN & Singles\\
\hline
MFGEKIND & Household without children\\
\hline
MFWEKIND & Household with children\\
\hline
MOPLHOOG & High level education\\
\hline
MOPLMIDD & Medium level education\\
\hline
MOPLLAAG & Lower level education\\
\hline
MBERHOOG & High status\\
\hline
MBERZELF & Entrepreneur\\
\hline
MBERBOER & Farmer\\
\hline
MBERMIDD & Middle management\\
\hline
MBERARBG & Skilled labourers\\
\hline
MBERARBO & Unskilled labourers\\
\hline
MSKA & Social class A\\
\hline
MSKB1 & Social class B1\\
\hline
MSKB2 & Social class B2\\
\hline
MSKC & Social class C\\
\hline
MSKD & Social class D\\
\hline
MHHUUR & Rented house\\
\hline
MHKOOP & Home owners\\
\hline
MAUT1 & 1 car\\
\hline
MAUT2 & 2 cars\\
\hline
MAUT0 & No car\\
\hline
MZFONDS & National Health Service\\
\hline
MZPART & Private health insurance\\
\hline
MINKM30 & Income < 30.000\\
\hline
MINK3045 & Income 30-45.000\\
\hline
MINK4575 & Income 45-75.000\\
\hline
MINK7512 & Income 75-122.000\\
\hline
MINK123M & Income >123.000\\
\hline
MINKGEM & Average income\\
\hline
MKOOPKLA & Purchasing power class\\
\hline
PWAPART & Contribution private third party insurance\\
\hline
PWABEDR & Contribution third party insurance (firms)\\
\hline
PWAAND & Contribution third party insurane (agriculture)\\
\hline
PPERSAUT & Contribution car policies\\
\hline
PBESAUT & Contribution delivery van policies\\
\hline
PMOTSCO & Contribution motorcycle/scooter policies\\
\hline
PVRAAUT & Contribution lorry policies\\
\hline
PAANHANG & Contribution trailer policies\\
\hline
PTRACTOR & Contribution tractor policies\\
\hline
PWERKT & Contribution agricultural machines policies\\
\hline
PBROM & Contribution moped policies\\
\hline
PLEVEN & Contribution life insurances\\
\hline
PPERSONG & Contribution private accident insurance policies\\
\hline
PGEZONG & Contribution family accidents insurance policies\\
\hline
PWAOREG & Contribution disability insurance policies\\
\hline
PBRAND & Contribution fire policies\\
\hline
PZEILPL & Contribution surfboard policies\\
\hline
PPLEZIER & Contribution boat policies\\
\hline
PFIETS & Contribution bicycle policies\\
\hline
PINBOED & Contribution property insurance policies\\
\hline
PBYSTAND & Contribution social security insurance policies\\
\hline
AWAPART & Number of private third party insurance\\
\hline
AWABEDR & Number of third party insurance (firms)\\
\hline
AWALAND & Number of third party insurane (agriculture)\\
\hline
APERSAUT & Number of car policies\\
\hline
ABESAUT & Number of delivery van policies\\
\hline
AMOTSCO & Number of motorcycle/scooter policies\\
\hline
AVRAAUT & Number of lorry policies\\
\hline
AAANHANG & Number of trailer policies\\
\hline
ATRACTOR & Number of tractor policies\\
\hline
AWERKT & Number of agricultural machines policies\\
\hline
ABROM & Number of moped policies\\
\hline
ALEVEN & Number of life insurances\\
\hline
APERSONG & Number of private accident insurance policies\\
\hline
AGEZONG & Number of family accidents insurance policies\\
\hline
AWAOREG & Number of disability insurance policies\\
\hline
ABRAND & Number of fire policies\\
\hline
AZEILPL & Number of surfboard policies\\
\hline
APLEZIER & Number of boat policies\\
\hline
AFIETS & Number of bicycle policies\\
\hline
AINBOED & Number of property insurance policies\\
\hline
ABYSTAND & Number of social security insurance policies\\
\hline
CARAVAN & Number of mobile home policy\\
\hline
\end{longtable}
